A bird’s-eye view on the habitability of exoplanets via statistical learning techniques

### 2020-10-27 Discussion/Presentation.tex
PUB

\documentclass[compress]{beamer}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{varwidth}
\usepackage{beamerthemesplit}

@@

\begin{frame}
\frametitle{Theoretical background - Star features }
\begin{columns}
\column{0.4\textwidth}
\begin{itemize}
\item \textbf{Main features}: For this work the main features of star are the stellar luminosity, its temperature and spectral type
\item\textbf{H-R diagram}: with these features the Hertzsprung-Russell diagram classify the stars (the temperature and spectral type of a star are two faces of the same medal)
\end{itemize}
\column{0.45\textwidth}
\includegraphics[width=\linewidth,]{Pic/S_T_T_explanation.png}
\begin{center}
Image taken from \cite{HR_diagram}
\end{center}
\end{columns}
\end{frame}

@@

>>>>

\documentclass[compress]{beamer}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\author{Marzio De Corato}
\usepackage{varwidth}
\usepackage{beamerthemesplit}

@@

\begin{frame}
\frametitle{Theoretical background - Star features }
\begin{columns}
\column{0.4\textwidth}
\begin{itemize}
\item \textbf{Main features}: For this work the main features of star are the stellar luminosity (S\_L), its temperature (S\_T) and spectral type (S\_S\_T)
\item\textbf{H-R diagram}: with these features the Hertzsprung-Russell diagram classify the stars (the temperature and spectral type of a star are two faces of the same medal)
\end{itemize}
\column{0.45\textwidth}
\includegraphics[width=\linewidth,]{Pic/S_T_T_explanation.png}
\begin{center}
Image taken from \cite{HR_diagram}
\end{center}
\end{columns}
\end{frame}

@@

\section{Data inspection}
\subsection{Densities}
\begin{frame}
\frametitle{Data inspection - densities}
\begin{columns}[t]
        \column{.25\textwidth}
        \includegraphics[width=\linewidth]{Pic/Density/P_M.pdf}
        \begin{center}
        Planet mass\\
        \end{center}
        \includegraphics[width=\linewidth]{Pic/Density/P_A.pdf}
        \begin{center}
        Planet apastron\\
        \end{center}
        \column{.25\textwidth}
        \includegraphics[width=\linewidth]{Pic/Density/P_R.pdf}
        \begin{center}
        Planet radius\\
        \end{center}
        \includegraphics[width=\linewidth]{Pic/Density/P_D.pdf}
        \begin{center}
        Planet distance\\
        \end{center}
        \column{.25\textwidth}
        \includegraphics[width=\linewidth]{Pic/Density/S_T.pdf}
        \begin{center}
        Stellar T \\
        \end{center}
        \includegraphics[width=\linewidth]{Pic/Density/P_PN.pdf}
        \begin{center}
        Planet periastron\\
        \end{center}
        \column{.25\textwidth}
        \includegraphics[width=\linewidth]{Pic/Density/P_T_E.pdf}
        \begin{center}
        P T E\\
        \end{center}
        \includegraphics[width=\linewidth]{Pic/Density/S_R_E.pdf}
        \begin{center}
        Star radius\\
        \end{center}
    \end{columns}
\end{frame}

\subsection{FAMD}
\begin{frame}
\frametitle{Data inspection - FAMD}
\begin{columns}
\column{0.5\textwidth}
\begin{center}
\includegraphics[width=\linewidth]{Pic/FAMD_squared_loadings.pdf}
\end{center}
\column{0.5\textwidth}
\begin{center}
\includegraphics[width=0.7\linewidth]{Pic/FAMD_Qualitative_VAR.pdf}
\includegraphics[width=0.7\linewidth]{Pic/FAMD_quantitative_variables.pdf}
\end{center}
\end{columns}
\end{frame}
